Appendix to ``A longitudinal analysis of the social information in infants' naturalistic

### 2022-01-07 paper/manuscript/appendix.Rmd
figure tweaks

---
title: "Appendix"
author: "Bria Long"
date: "1/6/2022"
output: word_document
---

@@

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=12) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  theme_few(base_size=12) +
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

ggpubr::ggarrange(p1, p2)
ggsave('appendix_figs/op_falsepositives.pdf', width = 7, height = 3)

@@

```{r}
summary_by_age_days_gold <- gold_sample %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(face_present_ketan), 
            num_hands = sum(hand_present_ketan), 
            num_detect = n()) %>%
  mutate(prop_faces = num_faces / num_detect, 
         prop_hands = num_hands / num_detect) %>%
  select(prop_faces, prop_hands, age_days, child_id) %>%
  pivot_longer(col = c(prop_faces, prop_hands), names_to="region", values_to = "prop")

summary_by_age_days_gold$age_scale <- scale(summary_by_age_days_gold$age_days, scale = FALSE)[,1] / 30.3
```

```{r}

## add face vs. hands model on gold sample to sanity check
diff_model2_gold <- summary(lmer(prop ~ region*poly(age_scale, 2) + (1 | child_id), data = summary_by_age_days_gold))

xtable(diff_model2_gold$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces and hands seen by infants based on human annotations.")

@@

# multi-location videos
meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
                     Activity!="Gesturing", Activity!="Look and Listen", 
                     Location!="N/A", Location!="California Room",
                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave('appendix_figs/activities_by_location.pdf', width = 7, height = 4)

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
# normalize by location
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

ggsave('face_hand_by_motor.pdf', width=7, height=5)
```

>>>>

---
title: "Appendix to ``A longitudinal analysis of the social information in infants' naturalistic
  visual experience using automated detections''"
date: "1/6/2022"
output: word_document
---

@@

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  tidyr::replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + 
theme_few(base_size=12) +
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=top+0.5*height) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
   theme_few(base_size=12) +
  xlab("Center of OpenPose Detection") + 
  ylab("Center of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse() + xlim(-.05,1.05) + ylim(1.05,-.05)

ggpubr::ggarrange(p1, p2)
ggsave('appendix_figs/op_falsepositives.pdf', width = 7, height = 3.4)

@@

@@

# multi-location videos
meta_long %>% filter(Activity!="N/A", Activity!="Consequence", Activity!="Kicking",
                     Activity!="Gesturing", Activity!="Look and Listen", 
                     Location!="N/A", Location!="California Room",
                     Location!="Rapidly Moving Between Locations", Location!="Piano Room") %>%
  mutate(Location = ifelse(Location=="Dog Park/Park/Field", "Off Property", Location)) %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Activity, y=Location, fill=n)) +
  geom_tile() + theme_few(base_size=11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave('appendix_figs/activities_by_location.pdf', width = 8, height = 4)

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Probability of different activities, given location (in single-location videos)."}
# normalize by location
meta_long_1loc %>% 
  mutate(Location = factor(Location, levels=names(loc_freq))) %>%
  left_join(meta_long_1loc %>% group_by(Location) %>% summarise(loc_freq = n())) %>%
  group_by(Activity, Location) %>%
  summarise(n = n(),
            prop_loc = n / loc_freq) %>% 
  ggplot(aes(x=Activity, y=Location, fill=prop_loc)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave('appendix_figs/prob_activity_by_single_location.pdf', width = 8, height = 4)
```

@@

ggsave('appendix_figs/face_hand_by_motor.pdf', width=7, height=5)
```
